---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r options, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

set.seed(1337)
```

RDP
===

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/RDP)](https://CRAN.R-project.org/package=RDP)
[![R build status](https://github.com/robertdj/RDP/workflows/R-CMD-check/badge.svg)](https://github.com/robertdj/RDP/actions)
[![Codecov test coverage](https://codecov.io/gh/robertdj/RDP/branch/main/graph/badge.svg)](https://codecov.io/gh/robertdj/RDP)
<!-- badges: end -->

The {RDP} package contains an implementation of the [Ramer–Douglas–Peucker algorithm
](https://en.wikipedia.org/wiki/Ramer%E2%80%93Douglas%E2%80%93Peucker_algorithm) for reducing the number of points in a curve.

There are other R packages that offer implementations of the Ramer–Douglas–Peucker algorithm, but {RDP} has only a single dependency and it executes pretty fast.


# Installation

{RDP} is [available on CRAN](https://cran.r-project.org/package=RDP) and can be installed with the command

``` r
install.packages("RDP")
```

{RDP} can also be installed from GitHub with the [{remotes} package](https://remotes.r-lib.org) using this command:

``` r
remotes::install_github("robertdj/RDP")
```


# Example

There is a single function in the {RDP} package.
Here is an example from the Wikipedia page linked to above with a description of the algorithm.
The original line is black and the approximating line is red.

```{r example}
x <- seq(from = 0, to = 5, by = 0.01)
y <- exp(-x) * cos(2 * pi * x)
plot(x, y, type = "l")

lines(RDP::RamerDouglasPeucker(x, y, 0.06), col = "red", lty = 2)
```


# Performance

Here is a comparison of the execution speed and memory usage of the {RDP} implementation and a pure R implementation from the [{kmlShape} package](https://cran.r-project.org/package=kmlShape):

```{r timing}
x <- as.double(1:10^4)
y <- rnorm(length(x))
bench::mark(
    RDP = RDP::RamerDouglasPeucker(x, y, epsilon = 0.1),
    kmlShape = kmlShape::DouglasPeuckerEpsilon(x, y, epsilon = 0.1)
)
```

In this example we see from the [{bench} package](https://bench.r-lib.org) summary that {RDP} is several 1000 times faster and only use a fraction of the memory.


# Acknowledgements

The C++ code was *originally* based on [a Gist from TimSC](https://gist.github.com/TimSC/0813573d77734bcb6f2cd2cf6cc7aa51), but over time it has been almost completely rewritten.

