---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(magrittr)
```

RDP
===

<!-- badges: start -->
[![R build status](https://github.com/robertdj/RDP/workflows/R-CMD-check/badge.svg)](https://github.com/robertdj/RDP/actions)
[![Codecov test coverage](https://codecov.io/gh/robertdj/RDP/branch/master/graph/badge.svg)](https://codecov.io/gh/robertdj/RDP?branch=main)
<!-- badges: end -->

The {RDP} package contains an implementation of the [Ramer–Douglas–Peucker algorithm
](https://en.wikipedia.org/wiki/Ramer%E2%80%93Douglas%E2%80%93Peucker_algorithm) for reducing the number of points in a curve.

There are other R packages that offer implementations of the Ramer–Douglas–Peucker algorithm, but {RDP} has only a single dependency and it executes pretty fast.


# Installation

{RDP} is only available on GitHub and can be installed with the [remotes package](https://remotes.r-lib.org) using this command:

``` r
remotes::install_github("robertdj/RDP")
```


# Example

There is a single function in the {RDP} package.
Here is a comparison (using the [{bench} package](https://bench.r-lib.org)) of the execution speed and memory usage between the {RDP} implementation and a pure R implementation in the [kmlShape package](https://cran.r-project.org/package=kmlShape):

```{r timing}
x <- as.double(0:10^4)
y <- rnorm(length(x))
bench::mark(
    RDP::RamerDouglasPeucker(x, y, epsilon = 0.1),
    kmlShape::DouglasPeuckerEpsilon(x, y, epsilon = 0.1)
) %>% 
    dplyr::select(expression, min, median, mem_alloc)
```

Here {RDP} is rougly 1000 times faster and using 10 % of the memory.
The outputs are identical (according to `dplyr::all_equal`).


# Acknowledgements

The C++ code is based on [a Gist from TimSC](https://gist.github.com/TimSC/0813573d77734bcb6f2cd2cf6cc7aa51).
At the time of implementation the code in the Gist is released under CC0. 
This makes it [compatible with the GPL](https://www.gnu.org/licenses/license-list.en.html#GPLCompatibleLicenses) -- as is required for compiled code linking against R.

